Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-05 WSSSPE1_report/WSSSPE1_summary_report.tex
Adding text to bibliography for communities.

\subsubsection{Resources for learning about software communities}
\begin{itemize}
\item academic fields studying communities (and software communities).
\item courses on online communities
\item need for software carpentry module on organizing communities?
\item \cite{howison_scientific_2011}
\item \cite{citeulike:11831265}
\item \cite{citeulike:7888211}
\item \cite{citeulike:478633}
\item \cite{opac-b1134063}
\item \cite{DBLP:conf/cscw/HowisonH11}
\item \cite{DBLP:conf/cscw/2011}
\item \cite{Trapani:2011}
\item \cite{Allsopp:2012}
\item \cite{1749-4699-6-1-015010}
\item \cite{Turk:2013:SCH:2484762.2484782}
\end{itemize}

>>>>

\subsubsection{Resources for learning about software communities}

Scientific software communities were viewed as a subset of software communities
as whole.  As such, resources applicable to generic software communities --
such as open source and proprietary technology companies -- can be used as
input and as guiding understanding of how to steward and develop scientific
software communities.  Because incentive structures are different in industry
and volunteer-based open source communities, these can provide rough guidelines
but not necessarily identically applicable.  The analogy between corporations
and scientific investigators (particularly in terms of competition, cooperation
and competitive advantage) has been explored in the literature below, but
because of the different incentive structure the analogy is not universally
true.

The literature below, suggested by attendees, addresses both non-scientific
software projects, as well as scientific projects.  The selections address both
descriptive and prescriptive approaches to communities.

\begin{itemize}
\item \cite{howison_scientific_2011}
\item \cite{citeulike:11831265}
\item \cite{citeulike:7888211}
\item \cite{citeulike:478633}
\item \cite{opac-b1134063}
\item \cite{DBLP:conf/cscw/HowisonH11}
\item \cite{DBLP:conf/cscw/2011}
\item \cite{Trapani:2011}
\item \cite{Allsopp:2012}
\item \cite{1749-4699-6-1-015010}
\item \cite{Turk:2013:SCH:2484762.2484782}
\end{itemize}
